Fourmile Calibrations and Output

### 2024-07-19 fourmile_outputs_2013edits.Rmd
updated a spelling error

ggplot(flow_plot_updated, aes(x = model_run, y = year, fill = pbias)) +
  geom_tile(color = "white") +
   scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = 0, name = "Ppias") +
  geom_text(aes(label = round(pbias, 2)), color = "black", size = 2.5) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Year")

>>>>

ggplot(flow_plot_updated, aes(x = model_run, y = year, fill = pbias)) +
  geom_tile(color = "white") +
   scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = 0, name = "Pbias") +
  geom_text(aes(label = round(pbias, 2)), color = "black", size = 2.5) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Year")
